Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-18 article_review/Manuscript.tex
More reviewer changes

An inherent practical problem of this estimation is how to quantify the number of model evaluations needed to ensure that estimates satisfy a desired error tolerance. This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices. Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.

@@

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \iid \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subsetneq u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can define the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subseteq \mathcal{D}.\]

@@

For $\ell,m \in \mathbb{N}_0$ and $\ell \le m$ we introduce the following notation,
\begin{align*}
S_m(f) &=  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \absolute{\hf_{\kappa}}, \ 
\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \absolute{ \hf_{\kappa+\lambda b^{m}}}, \\
\wcS_m(f)&=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
\sum_{\kappa=b^{m}}^{\infty} \absolute{\hf_{\kappa}},\\ 
\tS_{\ell,m}(f) &= \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \absolute{\tf_{m,\kappa}}.
\end{align*}
\comment{Among these sums, one should notice that $\hS_{0,m}(f)$ corresponds to the error bound appearing in \eqref{mapped_error_bound}. Thus, $\wcS_m(f)$ is an infinite sum of Walsh coefficients that contain the error bound coefficients. To have a control on the decay rate of the coefficients, we also define the finite sum of true coefficients $S_m(f)$. Note that from these sums, we can only observe $\tS_{\ell,m}(f)$.  }

Finally, we define the set of functions $\cc$,
\begin{multline} \label{conecond}
\cc:=\{f \in \mathbb{L}^2(\cube) : \hS_{\ell,m}(f) \le \homega(m-\ell) \wcS_m(f),\ \ \ell \le m, \\
\wcS_m(f) \le \wcomega(m-\ell) S_{\ell}(f),\ \  \ell_* \le \ell \le m\}.
\end{multline}
for a fixed $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$. \comment{The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$. First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ in some sense, in particular it bounds $\hS_{0,m}(f)$. This means that we can use $\wcS_m(f)$ as an indicator of the error bound. Then, we also need $S_{\ell}(f)$ to bound $\wcS_m(f)$ which helps transforming the infinite sum into a finite sum. In this step, we are assuming that if $S_{\ell}(f)$ is small enough, we expect the high frequency coefficients, i.e. $\wcS_m(f)$, to also be small. By defining $r=m-\ell$, and assuming that $\homega(r)\wcomega(r)<1$ with $r\in\mathbb{N}$, one may intuitively see $r$ as a distance between $S_{\ell}(f)$ and $\wcS_m(f)$ to tune: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients. Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} With this reasoning, in \cite[Sec. 4.2]{HicJim} we showed that for any $f\in\cc$,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(r)}{1 - \homega(r) \wcomega(r)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
\end{equation}
where one may increase $m$ until the error bound {\color{purple}$\epsilon_{\widehat{I}}$} is small enough.

@@

Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
For the rest of the paper, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).

@@

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimension Sobol' sequence is generated based on the directional numbers found in \cite{Kuo}. These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
\end{equation*}
where $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. It requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
\bigskip

@@

The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and the integrands fall outside the cone \eqref{conecond}.

@@

The two classical test functions considered in this article are {\color{purple} (Lolo) a non QMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).

@@

{\color{purple} (Lolo)
The non QMC friendly version of the g-function is defined as follows:
\begin{equation*}
f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |3x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
\end{equation*}}
Each value $a_j$ determines the relative importance of the $x_j$. When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more influent. For this example, we chose $d=6$ and $a_1=0,a_2=0.5, a_3=3, a_4=9, a_5=99$, and $a_6=99$.

@@

The sequential estimation procedure proposed in this article offers a practical solution with the construction of an estimator and error bound for Sobol' indices. The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance. The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices. Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods. The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions. Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.

@@

\bibitem{Bratley}
Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
\bibitem{Forrester}
Forrester, A., S\'obester, A., Keane, A.: Engineering Design via Surrogate Modelling, Chichester: Wiley (2008)
\bibitem{Gilquin.rec}
Gilquin, L., Arnaud, E., Monod, H., Prieur, C.: Recursive estimation procedure of Sobol' indices based on replicated designs, preprint available at \url{https://hal.inria.fr/hal-01291769}, (2016).
\bibitem{GJAHMP}
Gilquin, L., Jim\'enez Rugama, Ll.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, C. R. Math., vol. 355, 10-14 (2017)
\bibitem{HicJim}
Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
\bibitem{HonHic00a}
H.S. Hong, F.J. Hickernell.: Algorithm 823: Implementing scrambled digital nets, ACM Trans. Math. Software, vol. 29, 95-109, (2003)
\bibitem{Hoeffding}
Hoeffding, W.F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
\bibitem{Janon}
Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
\bibitem{JimHic}
Jim\'enez Rugama, Ll.A., Hickernell, F.J.: Adaptive Multidimensional Integration Based on Rank-1 Lattices: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 407-422 (2016)
\bibitem{Kuo} S. Joe, F. Y. Kuo, Constructing Sobol Sequences with Better Two-Dimensional Projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
\bibitem{Lemieuxbook}
Lemieux,C.: Monte Carlo and Quasi-Monte Carlo Sampling, Springer, New-York (2009)
\bibitem{Mara}
Mara, T.A., Rakoto Joseph, 0.: Comparison of some efficient methods to evaluate the main effect of computer model factors, J. Statist. Comput. Simulation \textbf{78}(2), 167-178 (2008)
\bibitem{McKay}
McKay, M.D.: Evaluating prediction uncertainty, Los Alamos National Laboratory Report NUREG/CR- 6311, LA-12915-MS. (1995)
\bibitem{Niederreiter} 
Niederreiter, H.: Random Number Generation and Quasi-Monte Carlo Methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
\bibitem{Owe95}
A.B. Owen.: Randomly permuted $(t,m,s)$-nets and $(t,s)$-sequences: Monte Carlo and Quasi-Monte Carlo Methods in Scientific Computing, vol. 106, 299-317 (1995)
\bibitem{Owen}
Owen, A.B.: Better estimation of small Sobol' sensitivity indices, ACM Trans. Model. Comput. Simul. \textbf{23}(2), :11 (2013)
\bibitem{Saltelli}
Saltelli, A.: Making best use of models evaluations to compute sensitivity indices, Comput. Phys. Commun. \textbf{145}(2), 280-297 (2002)
\bibitem{Sobol'seq}
Sobol', I.M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
\bibitem{Sobol'}
Sobol', I.M.: Sensitivity indices for nonlinear mathematical models, Mathematical Modeling and Computational Experiment \textbf{1}, 407-414 (1993)
\bibitem{Tissot}
Tissot, J.Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2015)
\bibitem{Tong}
Tong C.: Self-validated variance-based methods for sensitivity analysis of model outputs, Reliab. Eng. Syst. Saf. \textbf{95}(3), 301-309 (2010)

>>>>

An inherent practical problem of this estimation is how to quantify the number of model evaluations needed to ensure that estimates satisfy a desired error tolerance. This article addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices. Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.

@@

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \sim \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subsetneq u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can define the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subseteq \mathcal{D}.\]

@@

For $\ell,m \in \mathbb{N}_0$ and $\ell \le m$ we introduce the following notation,
\begin{align*}
S_m(f) &=  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \absolute{\hf_{\kappa}}, \ 
\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \absolute{ \hf_{\kappa+\lambda b^{m}}}, \\
\wcS_m(f)&=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
\sum_{\kappa=b^{m}}^{\infty} \absolute{\hf_{\kappa}},\\ 
\tS_{\ell,m}(f) &= \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \absolute{\tf_{m,\kappa}}.
\end{align*}
\comment{The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$. Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} uses these symbols for the sums which should not be confused with the normalized Sobol' indices.

Among these sums, one should notice that $\hS_{0,m}(f)$ corresponds to the error bound appearing in \eqref{mapped_error_bound}. Thus, $\wcS_m(f)$ is an infinite sum of Walsh coefficients that contain the error bound coefficients. To have a control on the decay rate of the coefficients, we also define the finite sum of true coefficients $S_m(f)$. Note that from these sums, we can only observe $\tS_{\ell,m}(f)$.  }

Finally, we define the set of functions $\cc$,
\begin{multline} \label{conecond}
\cc:=\{f \in \mathbb{L}^2(\cube) : \hS_{\ell,m}(f) \le \homega(m-\ell) \wcS_m(f),\ \ \ell \le m, \\
\wcS_m(f) \le \wcomega(m-\ell) S_{\ell}(f),\ \  \ell_* \le \ell \le m\}.
\end{multline}
for a fixed $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$. \comment{The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$. First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ in some sense, in particular it bounds $\hS_{0,m}(f)$. This means that we can use $\wcS_m(f)$ as an indicator of the error bound. Then, we also need $S_{\ell}(f)$ to bound $\wcS_m(f)$ which helps transforming the infinite sum into a finite sum. In this step, we are assuming that if $S_{\ell}(f)$ is small enough, we expect the high frequency coefficients, i.e. $\wcS_m(f)$, to also be small. By defining $r=m-\ell$ with $\homega(r)\wcomega(r)<1$ and $r\in\mathbb{N}$, one may intuitively see $r$ as the distance between $S_{\ell}(f)$ and $\wcS_m(f)$. One only needs to choose the appropriate $r$: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients. Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} With this reasoning, in \cite[Sec. 4.2]{HicJim} we showed that for any $f\in\cc$,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
\le \tS_{m-r,m}(f)\underbrace{\frac{\homega(m) \wcomega(r)}{1 - \homega(r) \wcomega(r)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
\end{equation}
where one may increase $m$ until the error bound {\color{purple}$\epsilon_{\widehat{I}}$} is small enough.

@@

Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
\comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$. Nevertheless, some data-based necessary conditions are provided in \cite{HicJimLi}. These conditions can be used to automatically enlarge the cone according to each integrand.} For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).

@@

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimension Sobol' sequence is generated based on the directional numbers found in \cite{Kuo}. These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.......}

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
\end{equation*}
\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. For our algorithm, we extend Owen's estimator by replacing the uniform points with a Sobol' sequence in dimension $3d$. In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
\bigskip

@@

\comment{For the following examples we do not know the true Walsh coefficients of the integrands. Therefore, we cannot say whether they lie inside the cone defined. }The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and the integrands fall outside the cone \eqref{conecond}.

@@

The two classical test functions considered in this article are {\color{purple} (Lolo) a non qMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).

@@

{\color{purple} (Lolo)
The non qMC friendly version of the g-function is defined as follows:
\begin{equation*}
f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |3x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
\end{equation*}}
Each value $a_j$ determines the relative importance of the $x_j$. When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more influent. For this example, we chose $d=6$ and $a_1=0,a_2=0.5, a_3=3, a_4=9, a_5=99$, and $a_6=99$.

@@

The sequential estimation procedure proposed in this article offers a practical solution with the construction of an estimator and error bound for Sobol' indices. The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance. The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices. Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods. The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions. Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.
\comment{Add that we can consider relative errors and reference ...}

@@

\bibitem{Bratley}
Bratley, P., Fox, B. L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
\bibitem{Forrester}
Forrester, A., S\'obester, A., Keane, A.: Engineering design via surrogate modelling, Chichester: Wiley (2008)
\bibitem{Gilquin.rec}
Gilquin, L., Arnaud, E., Monod, H., Prieur, C.: Recursive estimation procedure of Sobol' indices based on replicated designs, preprint available at \url{https://hal.inria.fr/hal-01291769}, (2016).
\bibitem{GJAHMP}
Gilquin, L., Jim\'enez Rugama, Ll. A., Arnaud, E., Hickernell, F. J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, C. R. Math., vol. 355, 10-14 (2017)
\bibitem{HicJim}
Hickernell, F. J., Jim\'enez Rugama, Ll. A.: Reliable adaptive cubature using digital sequences: Monte Carlo and Quasi-Monte Carlo Methods 2014, vol. 163, 367-383 (2016)
\bibitem{HicJimLi}
Hickernell, F. J., Jim\'enez Rugama, Ll. A., Li, D.: Adaptive quasi-Monte Carlo methods for cubature, preprint available at \url{https://arxiv.org/pdf/1702.01491.pdf}, (2017).
\bibitem{HonHic00a}
Hong, H. S., Hickernell, F. J.: Algorithm 823: Implementing scrambled digital nets, ACM Trans. Math. Software, vol. 29, 95-109, (2003)
\bibitem{Hoeffding}
Hoeffding, W. F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
\bibitem{Janon}
Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
\bibitem{JimHic}
Jim\'enez Rugama, Ll. A., Hickernell, F. J.: Adaptive multidimensional integration based on rank-1 lattices: Monte Carlo and Quasi-Monte Carlo Methods 2014, vol. 163, 407-422 (2016)
\bibitem{Kuo} Joe, S., Kuo, F. Y., Constructing Sobol sequences with better two-dimensional projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
\bibitem{Lemieuxbook}
Lemieux, C.: Monte Carlo and quasi-Monte Carlo sampling, Springer, New-York (2009)
\bibitem{Mara}
Mara, T. A., Rakoto Joseph, O.: Comparison of some efficient methods to evaluate the main effect of computer model factors, J. Statist. Comput. Simulation \textbf{78}(2), 167-178 (2008)
\bibitem{McKay}
McKay, M. D.: Evaluating prediction uncertainty, Los Alamos National Laboratory Report NUREG/CR- 6311, LA-12915-MS. (1995)
\bibitem{Niederreiter} 
Niederreiter, H.: Random number generation and quasi-Monte carlo methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
\bibitem{Owe95}
Owen, A. B.: Randomly permuted $(t,m,s)$-nets and $(t,s)$-sequences: Monte Carlo and Quasi-Monte Carlo Methods in Scientific Computing, vol. 106, 299-317 (1995)
\bibitem{Owen}
Owen, A.B.: Better estimation of small Sobol' sensitivity indices, ACM Trans. Model. Comput. Simul. \textbf{23}(2), :11 (2013)
\bibitem{Saltelli}
Saltelli, A.: Making best use of models evaluations to compute sensitivity indices, Comput. Phys. Commun. \textbf{145}(2), 280-297 (2002)
\bibitem{Sobol'seq}
Sobol', I. M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
\bibitem{Sobol'}
Sobol', I. M.: Sensitivity indices for nonlinear mathematical models, Mathematical Modeling and Computational Experiment \textbf{1}, 407-414 (1993)
\bibitem{Tissot}
Tissot, J. Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2015)
\bibitem{Tong}
Tong, C.: Self-validated variance-based methods for sensitivity analysis of model outputs, Reliab. Eng. Syst. Saf. \textbf{95}(3), 301-309 (2010)
